Repairing cooperation through a cognitive intervention in the repeated Trust Game

### 2023-05-23 article.Rmd
fixed title Latex

---
title: Repairing cooperation through a cognitive intervention in the repeated Trust Game
subtitle: 
titlerunning: 
authorrunning: 
# thanks: The authors have no conflicts of interest to declare that are relevant to the content of this article. This work was supported by the UK Engineering and Physical Sciences Research Council under grant EP/S515255/1.

authors:
- name: Ismail Guennouni
  address: Department of Experimental Psychology, University College London, 26 Bedford Way, London WC1H 0AP, United Kingdom
  email: i.guennouni.17@ucl.ac.uk

- name: Maarten Speekenbrink
  address: Department of Experimental Psychology, University College London, 26 Bedford Way, London WC1H 0AP, United Kingdom
  email: m.speekenbrink@ucl.ac.uk

- name: Quentin Huys
  address: Max Planck Institute of Computational Psychiatry
  email: q.huys@ucl.ac.uk

- name: Samuel Dupret
  address: HLI
  email: sam.dupret@ucl.ac.uk

keywords:
- Economic Games 
- Hidden Markov Models
- Repair of Cooperation
- Cognitive Intervention

>>>>

---
title: "Repairing cooperation through a cognitive intervention in the repeated Trust Game"
author:
  - Ismail Guennouni
  - Maarten Speekenbrink
  - Quentin Huys
  - Samuel Dupret

# - name: Ismail Guennouni
#   address: Department of Experimental Psychology, University College London, 26 Bedford Way, London WC1H 0AP, United Kingdom
#   email: i.guennouni.17@ucl.ac.uk
# 
# - name: Maarten Speekenbrink
#   address: Department of Experimental Psychology, University College London, 26 Bedford Way, London WC1H 0AP, United Kingdom
#   email: m.speekenbrink@ucl.ac.uk
# 
# - name: Quentin Huys
#   address: Max Planck Institute of Computational Psychiatry
#   email: q.huys@ucl.ac.uk
# 
# - name: Samuel Dupret
#   address: HLI
#   email: sam.dupret@ucl.ac.uk
keywords:
- Economic Games 
- Hidden Markov Models
- Repair of Cooperation
- Cognitive Intervention
